---
title: "Severe Depression"
author: "Benjamin W Nelson"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Resources
https://stats.idre.ucla.edu/r/faq/random-coefficient-poisson-models/
https://glmmadmb.r-forge.r-project.org/
https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html
https://cran.r-project.org/web/packages/glmmTMB/glmmTMB.pdf

#Set Working Directory
```{r}
setwd("~/Desktop/Manuscripts/Suicide Trajectory")
```

# Load Packages_______________________________________
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidyr)
library(tidylog)
library(ggplot2)
library(dplyr)
library(psych)
library(lubridate)
library(summarytools)
library(styler)
library(readr)
library(janitor)
library(pacman)

library(corrplot)
library(zoo)
library(magrittr)
library(readr)
library(naniar)
library(car)
library(reshape2)
library(jmv)
library(sjPlot)
library(sjstats)
library(bigrquery)
library(lme4) #for estimating multilevel models
library(lmerTest) #for p-values added to lme4 output
library(texreg) #for better outputs
library(effects) #for visualizing multilevel model effects
library(sjstats) #might have to manually add
library(sjPlot) #Print results
library(sjlabelled) #Allows for custom printed results
library(sjmisc)
library(r2mlm)
library(merTools)
library(emmeans)
library(DHARMa) #model fit for mlm

#Set options
options(scipen = 999, digits = 3)
```

#Load Colors
```{r}
green1 <- "#67BF74"
green2 <- "#B4ECC0"
blue <- "#5DC0BD"
red <- "#CF4C24"
yellow <- "#F5C64E"

colors <- c(green1, green2, blue, red, yellow)
```


#Pull Data
#Redacting bigquery code
```{r, eval = FALSE}

```

#Data Cleaning
##Clean Demographics
```{r}
#Clean demo
demo_cleaned1 <- demo %>% 
  dplyr::select(userID,
                programID,
                sex,
                location,
                historyOfMajorTrauma,
                completion,
                programStartDate,
                programEndDate,
                age,
                daysactive,
                introvideoswatched,
                lastWeekNbr,
                initialOnsetDepressionEpisodeAge,
                majorDepressionEpisodes,
                psychiatricHospitalizations,
                suicideAttempts,
                medicationnew,
                meditationminutes,
                averagesdaysmessagessentperweek)

duplicated_demo_cleaned1 <- duplicated(demo_cleaned1[,c("userID", "programStartDate")])
freq(duplicated_demo_cleaned1)

#Remove Duplicate IDs
demo_cleaned2 <- demo_cleaned1 %>% 
  distinct(userID, programStartDate, .keep_all = TRUE)
```

##PHQ Create Total Score for 8 Items
```{r}
#See if any items are missing.
phq_data %>% 
  naniar::vis_miss()

#create dataframe of relevant variables that need to be summed
phq_8 <- data.frame(phq_data$question1, phq_data$question2, phq_data$question3, phq_data$question4, phq_data$question5, phq_data$question6, phq_data$question7, phq_data$question8) 

#No items are reverse scored
phq8_keys <- make.keys(phq_8, list(phq_8 = c(1, 2, 3, 4, 5, 6, 7, 8))) 

#Score and use median if missing data
phq_8_scale <- scoreItems(phq8_keys, phq_8, totals = TRUE, impute = "median")

#Save the scores back into the dataset
phq_data$phq8_total <- phq_8_scale[["scores"]]
```

##Merge PHQ and GAD
```{r}
phq_gad1 <- left_join(phq_data, gad_data, by = c("userID", "score_week", "date"))
```

###Only Keep Weeks 0 - 12 and 1, 3, 6, and 12 month followup
```{r}
#Any data collected up to 4 weeks before baseline, include as baseline
phq_gad1$score_week <- ifelse(phq_gad1$score_week >= -4 & phq_gad1$score_week <= 0, 0, as.numeric(phq_gad1$score_week))

#Recode Weeks 21-29 as 3 Month
phq_gad1$score_week <- ifelse(phq_gad1$score_week >= 21 & phq_gad1$score_week <= 29, 25, as.numeric(phq_gad1$score_week))

#Recode Weeks 32-44 as 6 Month
phq_gad1$score_week <- ifelse(phq_gad1$score_week >= 32 & phq_gad1$score_week <= 44, 38, as.numeric(phq_gad1$score_week))

#Recode Weeks 54-74 as 12 Month
phq_gad1$score_week <- ifelse(phq_gad1$score_week >= 54 & phq_gad1$score_week <= 74, 64, as.numeric(phq_gad1$score_week))


#phq_gad1$score_week[phq_gad1$score_week >= -4 & phq_gad1$score_week <= 0] <- 0

phq_gad2 <- phq_gad1 %>% 
  dplyr::filter(score_week == "0" | 
                  score_week == "1" | 
                  score_week =="2" | 
                  score_week == "3" | 
                  score_week =="4" | 
                  score_week == "5" | 
                  score_week =="6" | 
                  score_week == "7" | 
                  score_week =="8" | 
                  score_week == "9" | 
                  score_week =="10" | 
                  score_week == "11" | 
                  score_week == "12" | 
                  score_week == "13" |
                  score_week == "25" |
                  score_week == "38" |
                  score_week == "64") 

#Check Frequency of Week
summarytools::freq(phq_gad2$score_week)

#Recode Odd Weeks to Previous Even Week
phq_gad2$score_week[phq_gad2$score_week == 1] <- 2
phq_gad2$score_week[phq_gad2$score_week == 3] <- 2
phq_gad2$score_week[phq_gad2$score_week == 5] <- 4
phq_gad2$score_week[phq_gad2$score_week == 7] <- 6
phq_gad2$score_week[phq_gad2$score_week == 9] <- 8
phq_gad2$score_week[phq_gad2$score_week == 11] <- 10
phq_gad2$score_week[phq_gad2$score_week == 13] <- 12

#Check Frequency of Week
freq(phq_gad2$score_week)
```

###Check for PHQ and GAD Duplicates
```{r}
duplicated_phq_gad2 <- duplicated(phq_gad2[,c("userID", "score_week", "date")])
freq(duplicated_phq_gad2)

#Average Duplicate PHQ and GAD scores within the same week
phq_gad3 <- dplyr::summarize(dplyr::group_by(phq_gad2, userID, score_week, date),
                 phq_total_cleaned = mean(phqscore_overall, na.rm = TRUE),
                 gad_total_cleaned = mean(gadscore_overall, na.rm = TRUE),
                 phq_item9_cleaned = mean(question9, na.rm = TRUE),
                 phq_8_total = mean(phq8_total, na.rm = TRUE))

phq_gad_cleaned_duplicated <- duplicated(phq_gad3[,c("userID", "score_week", "date")])
freq(phq_gad_cleaned_duplicated)
```

###Add missing treatment weeks to each participant
```{r}
phq_gad3$date_numeric <- format(as.Date(phq_gad3$date, format="%d/%m/%Y"),"%Y")
phq_gad3$date_numeric <- as.numeric(phq_gad3$date_numeric)

phq_gad4 <- phq_gad3 %>% 
  tidyr::complete(userID, score_week = c(0, 2, 4, 6, 8, 10, 12, 25, 38))

duplicated_phq_gad4 <- duplicated(phq_gad4[,c("userID", "score_week", "date")])
freq(duplicated_phq_gad4)

phq_gad5 <- phq_gad4 %>% 
  distinct(userID, score_week, .keep_all = TRUE)
```

###Remove NaN
```{r}
phq_gad5$gad_total_cleaned[phq_gad5$gad_total_cleaned == "NaN"] <- NA
phq_gad5$phq_total_cleaned[phq_gad5$phq_total_cleaned == "NaN"] <- NA
```

##Clean Weekly Data
```{r}
weekly_data_long <- weekly_data %>% 
  pivot_longer(cols = c(-userID), names_sep="_(?=[^_]+$)", names_to = c(".value", "wave"))

weekly_data_long <- weekly_data_long %>% 
  rename(score_week = wave,
         daysactive_weekly = daysactive,
         messagessent_weekly = messagessent,
         hrvminutes_weekly = hrvminutes,
         meditationminutes_weekly = meditationminutes)

weekly_data_long$score_week <- as.numeric(weekly_data_long$score_week)
```

##Merge Data
```{r}
data1 <- left_join(phq_gad5, demo_cleaned2, by = "userID")

data1 <- left_join(data1, weekly_data_long, by = c("userID", "score_week"))

duplicated_data1 <- duplicated(data1[,c("userID", "score_week", "date")])
freq(duplicated_data1) #no duplicate
```

##Select Variables
```{r}
data2 <- data1 %>% 
  dplyr::select(userID,
                programID,
                sex,
                location,
                historyOfMajorTrauma,
                completion,
                programStartDate,
                programEndDate,
                date,
                date_numeric,
                medicationnew,
                score_week,
                age,
                daysactive_weekly,
                introvideoswatched,
                lastWeekNbr,
                initialOnsetDepressionEpisodeAge,
                majorDepressionEpisodes,
                psychiatricHospitalizations,
                suicideAttempts,
                meditationminutes_weekly,
                hrvminutes_weekly,
                messagessent_weekly,
                phq_total_cleaned,
                gad_total_cleaned,
                phq_item9_cleaned,
                phq_8_total
                ) %>% 
  dplyr::rename(phq_9_total = phq_total_cleaned,
                gad_total = gad_total_cleaned,
                phq_item9 = phq_item9_cleaned) %>% 
  dplyr::filter(location == "US",
                lastWeekNbr == "12",
                programEndDate <= as.Date("2020-12-01")) #Finished the program at least 6 months ago (week 32-44). 6 months from 6/1/21
```

##Filter by 2020
```{r}
#Carry dates forward per subject
data2$date_numeric <- format(as.Date(data2$programEndDate, format="%d/%m/%Y"),"%Y")
data2$date_numeric <- as.numeric(data2$date_numeric)

data2$date_numeric <- DescTools::LOCF(data2$date_numeric)

data3 <- data2 %>% 
  dplyr::filter(date_numeric == "2020" | date_numeric == "2021")

duplicated_data3 <- duplicated(data3[,c("userID", "score_week", "date")])
freq(duplicated_data3) #no duplicate data
```

##Check Structure
```{r}
str(data3)

data3 <- as.data.frame(data3)

#Make Variables Factor
data3[,1:6] <- lapply(data3[,1:6], as.factor)

#Make Variables Numeric
data3[,12:27] <- lapply(data3[,12:27], as.numeric)
```

##Clean Age
```{r}
data3$age[data3$age <= -41] <- NA
data3$age[data3$age <= 0] <- NA
```

##Recode Number of MDD to Single vs Recurrent
```{r}
data4 <- data3 %>%
    mutate(mdd_episodes = case_when(
      majorDepressionEpisodes == 0 ~ 0,
      majorDepressionEpisodes == 1 ~ 1,
       majorDepressionEpisodes >= 2 ~ 2))

data4$mdd_episodes <- factor(data4$mdd_episodes,
                                      levels = c(0, 1, 2),
                                      labels = c("No Depression", "One MDD Episode", "Recurrent MDD"))
```

##Recode Number of Psychiatric Hospitalizations
```{r}
data5 <- data4 %>%
    mutate(psych_hospitalization_hx = case_when(
      psychiatricHospitalizations == 0 ~ 0,
      psychiatricHospitalizations >= 1 ~ 1))

data5$psych_hospitalization_hx <- factor(data5$psych_hospitalization_hx,
                                      levels = c(0, 1),
                                      labels = c("None", "Present"))
```

##Recode Number of Suicide Attempts
```{r}
data6 <- data5 %>%
    mutate(suicide_attempt_hx = case_when(
      suicideAttempts == 0 ~ 0,
      suicideAttempts >= 1 ~ 1))

data6$suicide_attempt_hx <- factor(data6$suicide_attempt_hx,
                                      levels = c(0, 1),
                                      labels = c("None", "Present"))
```

##Recode Medication to Yes or No
```{r}
#Recode so that no, No, and NA stay the same, but any other text gets 1
data6$meds <- ifelse(data6$medicationnew %in% c('no', "No", "false", NA, ""), data6$medicationnew, 1)

#Replace nos with 0
data6$meds[which(data6$meds == "no")] <- 0
data6$meds[which(data6$meds == "No")] <- 0
data6$meds[which(data6$meds == "false")] <- 0


data6$meds <- factor(data6$meds,
                     levels = c(0, 1),
                     labels = c("No Meds", "Meds"))
```

##Create Starting PHQ-9 Groups
```{r}
phq_baseline_sxs_group <- data6 %>%
  dplyr::filter(score_week == 0) %>% 
  dplyr::select(userID, score_week, phq_9_total) %>% 
  mutate(sxs_severity = case_when(
    phq_9_total <= 4 ~ 0,
    phq_9_total >= 5 & phq_9_total <= 9 ~ 1,
    phq_9_total >= 10 & phq_9_total <= 14 ~ 2,
    phq_9_total >= 15 & phq_9_total <= 19 ~ 3,
    phq_9_total >= 20 ~ 4))

phq_baseline_sxs_group$sxs_severity <- factor(phq_baseline_sxs_group$sxs_severity,
                                      levels = c(0, 1, 2, 3, 4),
                                      labels = c("Minimal", "Mild", "Moderate", "Moderately Severe", "Severe"))

phq_baseline_sxs_group <- phq_baseline_sxs_group %>% 
  dplyr::select(-c(score_week, phq_9_total))


data7 <- left_join(data6, phq_baseline_sxs_group, by = "userID")
```

##Create Starting PHQ-8 Groups
```{r}
phq8_baseline_sxs_group <- data7 %>%
  dplyr::filter(score_week == 0) %>% 
  dplyr::select(userID, score_week, phq_8_total) %>% 
  mutate(phq8_sxs_severity = case_when(
    phq_8_total <= 4 ~ 0,
    phq_8_total >= 5 & phq_8_total <= 9 ~ 1,
    phq_8_total >= 10 & phq_8_total <= 14 ~ 2,
    phq_8_total >= 15 & phq_8_total <= 19 ~ 3,
    phq_8_total >= 20 ~ 4))

phq8_baseline_sxs_group$phq8_sxs_severity <- factor(phq8_baseline_sxs_group$phq8_sxs_severity,
                                      levels = c(0, 1, 2, 3, 4),
                                      labels = c("None", "Mild", "Moderate", "Moderately Severe", "Severe"))

phq8_baseline_sxs_group <- phq8_baseline_sxs_group %>% 
  dplyr::select(-c(score_week, phq_8_total))

data8 <- left_join(data7, phq8_baseline_sxs_group, by = "userID")

data8 <- data8 %>% 
  dplyr::filter(score_week != 64)
```

#Check Missing Data
```{r}
#Overall missing data
data_missing <- data8 %>% 
  dplyr::select(userID,
                completion,
                sex,
                score_week,
                age,
                historyOfMajorTrauma,
                mdd_episodes,
                psych_hospitalization_hx,
                suicide_attempt_hx,
                phq8_sxs_severity,
                phq_8_total,
                phq_item9,
                meds,
                meditationminutes_weekly,
                messagessent_weekly,
                hrvminutes_weekly,
                introvideoswatched,
                daysactive_weekly) 

data_missing %>% 
  naniar::vis_miss()

#Combination of missing data
data_missing %>% 
  naniar::gg_miss_upset()

#Count of missing data
naniar::gg_miss_var(data_missing, score_week)
naniar::gg_miss_var(data_missing, completion)

#Examine missingness by variables
ggplot(data = data_missing, aes(x = score_week, y = phq_item9)) +
  naniar::geom_miss_point()

#Distribution of missing data
data_missing %>% 
  naniar::bind_shadow() %>% 
  ggplot(aes(x = score_week, fill = phq_item9_NA)) +
  geom_density(alpha = 0.4)
```

##Check Missingness
```{r}
imputation_data <- data8 %>% 
  dplyr::select(userID,
                completion,
                sex,
                age,
                historyOfMajorTrauma,
                mdd_episodes,
                psych_hospitalization_hx,
                suicide_attempt_hx,
                phq8_sxs_severity,
                phq_8_total,
                gad_total,
                phq_item9,
                meds,
                meditationminutes_weekly,
                messagessent_weekly,
                hrvminutes_weekly,
                introvideoswatched,
                daysactive_weekly)

imputation_data %>% 
  naniar::mcar_test()

imputation_data$userID <- as.integer(imputation_data$userID)
```

##Imputation
```{r}
set.seed(123)

all_imputations <- mice::mice(imputation_data, maxit= 10, m = 10) #MaxNWts = 2000

merged_imputations <- sjmisc::merge_imputations(
  imputation_data,
  all_imputations,
  ori = data8,
  summary = c("none", "dens", "hist", "sd"),
  filter = NULL
)
```

##Create New Variables
```{r}
#Proportion of Videos Watched
merged_imputations$intro_vid_imp_prop <- merged_imputations$introvideoswatched_imp/12
```

##Select Final Variables
```{r}
final_imputations <- merged_imputations %>% 
  dplyr::select(userID,
                completion,
                score_week,
                sex_imp,
                age_imp,
                historyOfMajorTrauma_imp,
                phq8_sxs_severity_imp,
                mdd_episodes_imp,
                psych_hospitalization_hx_imp,
                suicide_attempt_hx_imp,
                meds_imp,
                phq_8_total_imp,
                phq_item9_imp,
                meditationminutes_weekly_imp,
                messagessent_weekly_imp,
                hrvminutes_weekly_imp,
                daysactive_weekly_imp,
                intro_vid_imp_prop)

final_imputations %>% 
  naniar::vis_miss()

str(final_imputations)
```

#Descriptives
```{r}
psych::describeBy(final_imputations)
```

#Plot PHQ Across Treatment
```{r}
figure_data <- final_imputations %>% 
  dplyr::select(userID,
                score_week,
                phq8_sxs_severity_imp,
                phq_item9_imp)

figure_data <- na.omit(figure_data)

figure_data$userID <- as.factor(figure_data$userID)

figure_data$phq8_sxs_severity <- factor(figure_data$phq8_sxs_severity, levels = c("None", "Mild", "Moderate", "Moderately Severe", "Severe"))
levels(figure_data$phq8_sxs_severity)[levels(figure_data$phq8_sxs_severity) == "None"] <- "Less than Mild"


#Figure 1
phq_trajectory1 <- ggplot(data=subset(figure_data), aes(x = as.factor(score_week), y = phq_item9_imp, color = phq8_sxs_severity)) +
  geom_line(aes(group = userID), alpha = .1) + #This fades the individual lines
  geom_point(position=position_jitter(h=0.1, w=0.1), shape = 21, alpha = 0.5, size = 1) +
  stat_summary(data=subset(figure_data), aes(group=phq8_sxs_severity), fun=mean, geom="smooth", size = 2) + 
  theme(axis.ticks = element_line(colour = "black"), 
    panel.grid.major = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = "white"), 
    axis.title = element_text(size = 10), 
    axis.text = element_text(size = 10, colour = "black"), 
    axis.text.x = element_text(colour = "black"), 
    axis.text.y = element_text(colour = "black"), 
    plot.title = element_text(size = 10), 
    legend.text = element_text(size = 10), 
    legend.title = element_text(size = 10), 
    panel.background = element_rect(fill = "white"), 
    legend.key = element_rect(fill = "white"), 
    legend.background = element_rect(fill = "white")) +
  labs(title = "PHQ-9 Trajectory Across Treatment", x = "Treatment Week", y = "PHQ-9 9th Item", colour = "Symptom Severity") + 
  scale_color_manual(values = c("Severe" = "#CF4C24", "Moderately Severe" = "#32A3A1", "Moderate" = "#67BF74", "Mild" = "#5DC0BD", "Less than Mild" = "#F5C64E"))

phq_trajectory1
```

#Distributions
```{r}
boxplot(final_imputations$meditationminutes_weekly)
describe(final_imputations$meditationminutes)
meditation_min_ul <- 20.5 + (31.1*3)
meditation_min_ll <- 20.5 - (31.1*3)

boxplot(final_imputations$messagessent_weekly_imp)
describe(final_imputations$messagessent_weekly_imp)
message_ul <- 2.39 + (3.65*3)
message_ll <- 2.39 - (3.65*3)

boxplot(final_imputations$hrvminutes_weekly_imp)
describe(final_imputations$hrvminutes_weekly_imp)
hrv_ul <- 14.8 + (30*3)
hrv_ll <- 14.8 - (30*3)
```

##Winsorize
###Days Active
```{r}
final_imputations$meditationminutes_weekly_win <- DescTools::Winsorize(final_imputations$meditationminutes_weekly,
                                                                minval = meditation_min_ll,
                                                                maxval = meditation_min_ul)
boxplot(final_imputations$meditationminutes_weekly_win)

final_imputations$messagessent_weekly_imp_win <- DescTools::Winsorize(final_imputations$messagessent_weekly_imp,
                                                                              minval = message_ll,
                                                                              maxval = message_ul)
boxplot(final_imputations$messagessent_weekly_imp_win)

final_imputations$hrvminutes_weekly_imp_win <- DescTools::Winsorize(final_imputations$hrvminutes_weekly_imp,
                                                                minval = hrv_ll,
                                                                maxval = hrv_ul)
boxplot(final_imputations$hrvminutes_weekly_imp_win)
```

##Remove Week 64
```{r}
final_imputations <- final_imputations %>% 
  dplyr::filter(score_week != 64)
```

#Analyses

##Number of Subjects
```{r}
n_distinct(final_imputations$userID) #778 Participants

length(unique(final_imputations$userID)) #778 Participants

number_of_subjects <- final_imputations %>% 
  dplyr::filter(score_week == 0)

n_distinct(number_of_subjects$userID)
```

##Completed vs Dropout
```{r}
final_imputations %>% 
  dplyr::filter(score_week == 0) %>% 
  freq(completion)

completion_data <- final_imputations %>% 
  dplyr::filter(score_week == 0) %>% 
  filter(!is.na(completion)) %>% #Remove any missing
  filter(!is.na(sxs_severity)) %>% #Remove any missing
  group_by(sxs_severity) %>% #Group by parenting variable
  count(completion) %>% #create sum variable for each survey response
  mutate(percent = (n / sum(n)))

ggplot(completion_data, aes(fill=completion, y=percent, x=sxs_severity)) + 
  geom_bar(position="dodge", stat="identity") +
  ggtitle("Completion by Baseline Sxs Severity") +
  labs(x = NULL, y = NULL, fill = "Completion") +
  geom_text(aes(label = n), vjust = -.2, position = position_dodge(width = 1)) +
  scale_y_continuous(labels=scales::percent) + theme(panel.background = element_rect(fill = "white"))
```

##Descriptives
```{r}
descriptives_data <- final_imputations %>% 
  dplyr::filter(score_week == 0)

descriptives_data <- as.data.frame(descriptives_data)
```

###Symptom Severity
```{r}
freq(descriptives_data$phq8_sxs_severity_imp)
```

###PHQ Item 9 Distribution
```{r}
describe(final_imputations$phq_item9_imp)
```


###Table 1- Demographics
####Age
```{r}
describe(descriptives_data$age_imp)
```

####Sex
```{r}
freq(descriptives_data$sex_imp)
```

####Baseline PHQ-8
```{r}
describe(descriptives_data$phq_8_total_imp)

describeBy(descriptives_data$phq_8_total_imp, group = descriptives_data$phq8_sxs_severity_imp)
```

####Lifetime MDD Episodes
```{r}
freq(descriptives_data$mdd_episodes_imp)
```

####Meds
```{r}
freq(descriptives_data$meds_imp)
```

####Lifetime Suicide Attempt
```{r}
freq(descriptives_data$suicide_attempt_hx_imp)
```

####Lifetime Psychiatric Hospitalization
```{r}
freq(descriptives_data$psych_hospitalization_hx_imp)
```

####Lifetime History of Major Traumatic Event Exposure
```{r}
freq(descriptives_data$historyOfMajorTrauma_imp)
```

###Table 2. PHQ Item 9 Outcome Characteristics
####Frequency Pre and Post
```{r}
#Baseline
final_imputations %>% 
  dplyr::filter(score_week == 0) %>% 
                  freq(phq_item9_imp)

#End of Treatment
final_imputations %>% 
  dplyr::filter(score_week == 12) %>% 
                  freq(phq_item9_imp)

#3 Month Follow Up
final_imputations %>% 
  dplyr::filter(score_week == 25) %>% 
                  freq(phq_item9_imp)

#6 Month Follow Up
final_imputations %>% 
  dplyr::filter(score_week == 38) %>% 
                  freq(phq_item9_imp)
```


####Pre Post PHQ Change Effect Size
Hedges' g provides a bias correction to Cohen's d for small sample sizes. For sample sizes > 20, the results for both statistics are roughly equivalent. 

#####Overall Effect Size
```{r}
pre_post_data <- final_imputations %>% 
  dplyr::select(userID,
                score_week,
                phq_item9_imp) %>% 
  dplyr::filter(score_week == 0 | score_week == 12 | score_week == 25 | score_week == 38)

freq(pre_post_data$score_week)

#pre_post_data <- pre_post_data[-777,]


pre_post_data$score_week[pre_post_data$score_week == 0] <- "Baseline"
pre_post_data$score_week[pre_post_data$score_week == 12] <- "End of Treatment"
pre_post_data$score_week[pre_post_data$score_week == 25] <- "3 Month Follow-Up"
pre_post_data$score_week[pre_post_data$score_week == 38] <- "6 Month Follow-Up"
pre_post_data$score_week <- as.factor(pre_post_data$score_week)

pre_post_data$score_week <- factor(pre_post_data$score_week, levels = c("Baseline", "End of Treatment", "3 Month Follow-Up", "6 Month Follow-Up"))

describeBy(pre_post_data$phq_item9_imp, group = pre_post_data$score_week)

set.seed(123)

ggstatsplot::ggwithinstats(
  data = pre_post_data,
  x = score_week,
  y = phq_item9_imp,
  xlab = "Treatment Week",
  ylab = "Suicidal Ideation")

#Pre-Post Effect Size
pre_post_12_data <- pre_post_data %>% 
  dplyr::filter(score_week == "Baseline" | score_week == "End of Treatment")

effectsize::hedges_g(phq_item9_imp ~ score_week,
  data = pre_post_12_data,
  pooled_sd = TRUE,
  paired = TRUE,
  ci = 0.95)

#3 Month
pre_post_3mo_data <- pre_post_data %>% 
  dplyr::filter(score_week == "Baseline" | score_week == "3 Month Follow-Up")

effectsize::hedges_g(phq_item9_imp ~ score_week,
  data = pre_post_3mo_data,
  pooled_sd = TRUE,
  paired = TRUE,
  ci = 0.95)

#6 Month
pre_post_6mo_data <- pre_post_data %>% 
  dplyr::filter(score_week == "Baseline" | score_week == "6 Month Follow-Up")

effectsize::hedges_g(phq_item9_imp ~ score_week,
  data = pre_post_6mo_data,
  pooled_sd = TRUE,
  paired = TRUE,
  ci = 0.95)
```

#####Overall Effect Size Skewed
```{r}
set.seed(123)

ggstatsplot::ggwithinstats(
  data = pre_post_data,
  x = score_week,
  y = phq_item9_imp,
  xlab = "Treatment Week",
  ylab = "Suicidal Ideation",
  type = "nonparametric")

stats::friedman.test(phq_item9_imp ~ score_week | userID,
                     data = pre_post_data)

#Pre to Post
rstatix::wilcox_test(phq_item9_imp ~ score_week,
                        data = pre_post_12_data,
                        paired = TRUE)

rstatix::wilcox_effsize(phq_item9_imp ~ score_week,
                        data = pre_post_12_data,
                        paired = TRUE,
                        ci = TRUE,
                        ref.group = "Baseline")

ggstatsplot::ggwithinstats(
  data = pre_post_12_data,
  x = score_week,
  y = phq_item9_imp,
  xlab = "Treatment Week",
  ylab = "Suicidal Ideation",
  type = "nonparametric")

#Pre to 3 Month
pre_post_3mo_data <- final_imputations %>% 
  dplyr::select(userID,
                score_week,
                phq_item9_imp) %>% 
  dplyr::filter(score_week == 0 | score_week == 25)

pre_post_3mo_data$score_week[pre_post_3mo_data$score_week == 0] <- "Baseline"
pre_post_3mo_data$score_week[pre_post_3mo_data$score_week == 25] <- "3 Month Follow-Up"
pre_post_data$score_week <- as.factor(pre_post_data$score_week)

rstatix::wilcox_test(phq_item9_imp ~ score_week,
                        data = pre_post_3mo_data,
                        paired = TRUE)

rstatix::wilcox_effsize(phq_item9_imp ~ score_week,
                        data = pre_post_3mo_data,
                        paired = TRUE,
                        ci = TRUE,
                        ref.group = "Baseline")

ggstatsplot::ggwithinstats(
  data = pre_post_3mo_data,
  x = score_week,
  y = phq_item9_imp,
  xlab = "Treatment Week",
  ylab = "Suicidal Ideation",
  type = "nonparametric")

#Pre to 6 Month
pre_post_6mo_data <- final_imputations %>% 
  dplyr::select(userID,
                score_week,
                phq_item9_imp) %>% 
  dplyr::filter(score_week == 0 | score_week == 38)

pre_post_3mo_data$score_week[pre_post_3mo_data$score_week == 0] <- "Baseline"
pre_post_data$score_week[pre_post_data$score_week == 38] <- "6 Month Follow-Up"
pre_post_data$score_week <- as.factor(pre_post_data$score_week)

rstatix::wilcox_test(phq_item9_imp ~ score_week,
                        data = pre_post_3mo_data,
                        paired = TRUE)

rstatix::wilcox_effsize(phq_item9_imp ~ score_week,
                        data = pre_post_3mo_data,
                        paired = TRUE,
                        ci = TRUE,
                        ref.group = "Baseline")

ggstatsplot::ggwithinstats(
  data = pre_post_6mo_data,
  x = score_week,
  y = phq_item9_imp,
  xlab = "Treatment Week",
  ylab = "Suicidal Ideation",
  type = "nonparametric")
```

##Check PHQ Item 9 Dispursion
```{r}
describe(final_imputations$phq_item9_imp)
hist(final_imputations$phq_item9_imp)
boxplot(final_imputations$phq_item9_imp)
freq(final_imputations$phq_item9_imp)
```

##Functions
```{r}
#Singular means you haven a variance component that is sitting on 0. It may or may not impact estimates. Should figure out if you threw something in the model that is not useful
check_singularity <- function(lmerobj) {
  tt <- getME(lmerobj,"theta") #RE estimates
  ll <- getME(lmerobj,"lower") #lower bound on estimate
  
  #look for RE estimates that are very small (near zero) and the lower bound encompasses 0
  low_re <- tt[ll==0 & tt < 1e-2]
  return(low_re)
}
```

#Create Final Dataset for Treatment Weeks
```{r}
final_imputations_treatment <- final_imputations %>% 
  dplyr::filter(score_week != 25) %>% 
  dplyr::filter(score_week != 38)
```


##MLM
###Unconditional Model
```{r}
phq_model_unconditional <- lmer(phq_item9_imp ~ 1 + score_week + (1 + score_week | userID),
                                data = final_imputations_treatment)

summary(phq_model_unconditional)

final_imputations_treatment$score_week <- as.numeric(final_imputations_treatment$score_week )
```

###Model 1: Linear
```{r}
phq_model_linear <- lmer(phq_item9_imp ~ 1 + score_week +
                              sex_imp +
                              age_imp +
                              daysactive_weekly_imp +
                              mdd_episodes_imp +
                              psych_hospitalization_hx_imp +
                              suicide_attempt_hx_imp +
                              historyOfMajorTrauma_imp +
                              phq8_sxs_severity_imp +
                              meds_imp +
                           (1 + score_week | userID),
                           REML = TRUE,
                           data = final_imputations_treatment)

summary(phq_model_linear)
performance::r2(phq_model_linear)
performance::check_model(phq_model_linear)
performance::icc(phq_model_linear)
stats::AIC(phq_model_linear)
stats::BIC(phq_model_linear)
car::vif(phq_model_linear)
#variance inflation factor (VIF) is the quotient of the variance in a model with multiple terms by the variance of a model with one term alone. It quantifies the severity of multicollinearity in an ordinary least squares regression analysis. It provides an index that measures how much the variance (the square of the estimate's standard deviation) of an estimated regression coefficient is increased because of collinearity

#Individual Trajectories
individual_trajectories <- lattice::xyplot(phq_item9_imp ~ score_week|userID,
    data=final_imputations_treatment, type= c("p", "r"), #p is point and r is regression line
    col.line = "black",
    strip = FALSE,
    xlab="Treatment Week", ylab="Suicidal Ideation")

update(individual_trajectories, index.cond = function(x, y) coef(lm(y ~ x))[2])
```

##MLM Poisson

###Unconditional Model
```{r}
phq_model_unconditional_pos <- glmer(phq_item9_imp ~ 1 + score_week +  (1 + score_week| userID), 
                                family = poisson,
                                data = final_imputations_treatment)

summary(phq_model_unconditional_pos)
performance::check_overdispersion(phq_model_unconditional_pos)
```

###Linear Model Poisson
```{r}
phq_model_poisson <- glmmTMB(phq_item9_imp ~ 1 + score_week +
                               sex_imp +
                               age_imp +
                               daysactive_weekly_imp +
                               mdd_episodes_imp +
                               psych_hospitalization_hx_imp +
                               suicide_attempt_hx_imp +
                               historyOfMajorTrauma_imp +
                               phq8_sxs_severity_imp +
                               meds_imp +
                               (1 + score_week | userID),
                               data = final_imputations_treatment,
                               family=poisson)

summary(phq_model_poisson)
performance::r2(phq_model_poisson)
performance::check_model(phq_model_poisson)
performance::icc(phq_model_poisson)
stats::AIC(phq_model_poisson)
stats::BIC(phq_model_poisson)

#Alternative
phq_model_poisson_alt <- glmer(phq_item9_imp ~ 1 + score_week +
                                sex_imp +
                                age_imp +
                                mdd_episodes_imp + 
                                psych_hospitalization_hx_imp +
                                suicide_attempt_hx_imp +
                                historyOfMajorTrauma_imp + 
                                phq8_sxs_severity_imp + 
                                meds_imp +
                                (1 + score_week | userID),
                                family = poisson,
                                data = final_imputations_treatment)

summary(phq_model_poisson_alt)
stats::AIC(phq_model_poisson_alt)
```

##MLM Negative Binomial
```{r}
phq_model_nb <- glmer.nb(phq_item9_imp ~ 1 + score_week +
                               sex_imp +
                               age_imp +
                               daysactive_weekly_imp +
                               mdd_episodes_imp +
                               psych_hospitalization_hx_imp +
                               suicide_attempt_hx_imp +
                               historyOfMajorTrauma_imp +
                               phq8_sxs_severity_imp +
                               meds_imp +
                               (1 + score_week | userID),
                               data = final_imputations_treatment,
                         verbose=TRUE)

phq_model_nb_alt <- glmmTMB(phq_item9_imp ~ 1 + score_week +
                               sex_imp +
                               age_imp +
                               daysactive_weekly_imp +
                               mdd_episodes_imp +
                               psych_hospitalization_hx_imp +
                               suicide_attempt_hx_imp +
                               historyOfMajorTrauma_imp +
                               phq8_sxs_severity_imp +
                               meds_imp +
                               (1 + score_week | userID),
                               data = final_imputations_treatment,
                                family=nbinom2,
                        control = glmerControl(optimizer ="Nelder_Mead"))


summary(phq_model_nb)
performance::r2(phq_model_nb)
performance::check_model(phq_model_nb)
performance::icc(phq_model_nb)
performance::performance_aic(phq_model_nb)
stats::AIC(phq_model_nb)
stats::BIC(phq_model_nb)
```

#Compare Model Fits
```{r}
anova(phq_model_linear, phq_model_poisson, phq_model_nb) #Same fit

performance::compare_performance(phq_model_unconditional, phq_model_linear, phq_model_poisson, phq_model_nb, rank = TRUE)
```

#Print Tables
```{r}
tab_model(phq_model_linear, phq_model_poisson, phq_model_nb, 
          dv.labels = c("Linear Model", "Poisson Model", "Negative Binomial Model"),
          show.se = TRUE,
          show.std = TRUE,
          string.p = "P-Value",
          digits = 3,
          transform = NULL,
          file = "~/Desktop/Manuscripts/Suicide Trajectory/Tables/phq item 9 model final.doc")
```

#Reduction in Attempts and Deaths
See excel on Github
